---
title: "Thesis Analysis Script"
output: html_document
date: "2024-06-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


{r install packages}
install.packages("readxl")
install.packages("purrr")
install.packages("dplyr")
install.packages('stringr')


library(purrr)
library(readxl)
library(dplyr)
library(stringr)
library(kableExtra)
```{r}
library(purrr)
library(readxl)
library(dplyr)
library(stringr)
library(kableExtra)
```



```{r Loading Data}
# Load necessary libraries
library(dplyr)
library(readr)

# Initialize an empty list to store data frames
datasets <- list()

# Set directory path as object to reference
folder_path <- "G:/Experiment/Experiment/data"

# Get a list of CSV files in the folder
file_list <- list.files(path = folder_path, pattern = "\\.csv$", full.names = TRUE)

# Loop through each file, read it into a data frame, and store in the list
for (file in file_list) {
  # Create a name for the data frame by extracting the file name without extension
  df_name <- tools::file_path_sans_ext(basename(file))
  
  # Read the CSV file and assign it to a data frame
  df <- read_csv(file)
  
  # Add a 'participant' column to indicate the source of the data
  df <- df %>% mutate(participant = df_name)
  
  # Store the data frame in the list
  datasets[[df_name]] <- df
}

# Find common columns across all data frames
common_cols <- Reduce(intersect, lapply(datasets, colnames))

# Ensure that each common column has the same type across all data frames
for (col in common_cols) {
  col_types <- sapply(datasets, function(df) class(df[[col]]))
  if (length(unique(col_types)) > 1) {
    # Convert all to character if they have different types
    datasets <- lapply(datasets, function(df) {
      df[[col]] <- as.character(df[[col]])
      return(df)
    })
  }
}

# Combine all data frames in the list into one data frame
combined_df <- bind_rows(datasets)

#modify order of columns 
combined_df <- combined_df %>% select(participant, everything())

# Print the combined data frame
print(combined_df)



```

```{r remove NA}

initial_row_count <- nrow(combined_df)
cat("Initial row count:", initial_row_count, "\n")

# Remove non-trial rows
cleaned_data <- combined_df %>% filter(!is.na(trial))
rows_after_trial_filter <- nrow(cleaned_data)
cat("Rows removed as they did not correspond to a trial:", initial_row_count - rows_after_trial_filter, "\n")

# Remove practice trials
cleaned_data <- cleaned_data %>% filter(!(is.na(l_image) & is.na(beauty_text.started)))
rows_after_practice_filter <- nrow(cleaned_data)
cat("Rows removed by practice filter:", rows_after_trial_filter - rows_after_practice_filter, "\n")

# Final row count
cat("Final row count:", rows_after_practice_filter, "\n")

```


```{r Data Cleaning}
initial_row_count <- nrow(cleaned_data)
cat("Initial row count:", initial_row_count, "\n")

# Convert 'roi_targ2.timesOff' and 'roi_targ2.timesOn' to numeric
cleaned_data <- cleaned_data %>%
  mutate(
    roi_targ2.timesOn = as.numeric(roi_targ2.timesOn)
  )

# Remove rows where either 'roi_targ2.timesOff' or 'roi_targ2.timesOn' are NA after conversion
cleaned_data <- cleaned_data %>%
  filter(!is.na(roi_targ2.timesOn))

rows_after_trial_filter <- nrow(cleaned_data)
cat("Rows removed as roi_targ2.timeOn was NA Value :", initial_row_count - rows_after_trial_filter, "\n")

# Calculate 'SaccadicRT' and reorder columns
cleaned_data <- cleaned_data %>%
  mutate(SaccadicRTms = roi_targ2.timesOn * 1000) %>%
  select(participant, SaccadicRTms, everything())

row_count = nrow(cleaned_data)

cat("Final row count:", row_count, "\n")


```

```{r smaller df}
#create df with only the columns we need 
cleaned_data_small <- cleaned_data %>% select(participant, trial, TargX, DistX, l_image, r_image, roi_targ2.timesOn, roi_targ2.timesOff,SaccadicRTms)
```


########## Not applying this section as the Valuch et al paper did not do this######################
{r Remove outliers}
initial_row_count <- nrow(cleaned_data_small)
cat("trial count:", initial_row_count, "\n")

# Calculate Q1 (25th percentile) and Q3 (75th percentile)
Q1 <- quantile(cleaned_data_small$SaccadicRTms, 0.25)
Q3 <- quantile(cleaned_data_small$SaccadicRTms, 0.75)

# Calculate IQR (Interquartile Range)
IQR <- Q3 - Q1

# Define lower and upper bounds for outliers
lower_bound <- Q1 - 1.5 * IQR
upper_bound <- Q3 + 1.5 * IQR

# Filter out the outliers
cleaned_data_small <- cleaned_data_small[cleaned_data_small$SaccadicRTms >= lower_bound & cleaned_data_small$SaccadicRTms <= upper_bound, ]

rows_after_trial_filter <- nrow(cleaned_data_small)
cat("Trials removed as outliers :", initial_row_count - rows_after_trial_filter, "\n")

cat("% of Trials removed as outliers :", (initial_row_count - rows_after_trial_filter)/initial_row_count*100, "\n")

row_count = nrow(cleaned_data_small)

cat("Final trial count:", row_count, "\n")

```{r Add Target Sex column}
cleaned_data_small <- cleaned_data_small %>%
  mutate(targetsex = if_else(participant %in% c('pp1', 'pp4','pp7','pp9','pp11','pp10','pp16','pp17','pp21','pp23','pp26','pp28','pp29','pp30','pp32','pp33','pp36','pp37','pp38'), 'Male', 'Female'))
```

```{r split into male stim and female stim}
# Filter rows where participant is 'pp1' or 'pp4'
male_stim_data <- cleaned_data_small %>% filter(targetsex %in% c('Male'))

# Filter rows where participant is 'pp2', 'pp3', 'pp5', or 'pp6'
female_stim_data <- cleaned_data_small %>% filter(targetsex %in% c('Female'))

```


```{r assign target values}
malenames <- c('095m','098m','100m','108m','110m',"113m",'114m','115m', "116m", "117m",'119m','121m', "123m",'129m','147m','148m','149m',"151m",'152m','154m')
# Create the 'target' column based on the value in 'targX'
male_stim_data <- male_stim_data  %>%
  mutate(target = if_else(TargX == -0.45, l_image, r_image))

male_stim_data <- male_stim_data %>%
  mutate(targetraw = if_else(TargX == -0.45, l_image, r_image))

# Replace the entire cell with 'masculine' if it contains the word 'masc' etc
male_stim_data <- male_stim_data %>%
  mutate(target = if_else(str_detect(target, "masc"), "High Dimorphism", target))

male_stim_data <- male_stim_data %>%
  mutate(target = if_else(str_detect(target, "fem"), "Low Dimorphism", target))

male_stim_data <- male_stim_data %>%
  mutate(target = if_else(str_detect(target, "avg"), "Average", target))

male_stim_data <- male_stim_data %>%
  mutate(target = if_else(str_detect(target, "dist"), "Distinctive", target))

male_stim_data <- male_stim_data %>%
  mutate(target = if_else(str_detect(target, "/sym"), "Symmetrical", target))

male_stim_data <- male_stim_data %>%
  mutate(target = if_else(str_detect(target, "/asym"), "Asymmetrical", target))

#Trial remove tracker
initial_row_count <- nrow(male_stim_data)
cat("trial count:", initial_row_count, "\n")

#Remove reaction times that are too slow/fast (check values w/ jason)
male_stim_data <- male_stim_data %>% filter(SaccadicRTms > 50)

male_stim_data <- male_stim_data %>% filter(SaccadicRTms < 2000)

rows_after_trial_filter <- nrow(male_stim_data)
cat("Trials removed as SRTs too fast or slow :", initial_row_count - rows_after_trial_filter, "\n")

cat("% of Trials removed as SRTs too fast or slow :", (initial_row_count - rows_after_trial_filter)/initial_row_count*100, "\n")

row_count = nrow(male_stim_data)

cat("Final trial count:", row_count, "\n")


```

```{r assign target values}
# Create the 'target' column based on the value in 'targX'
femalenames <- c('003f','008f','010f','019f','020f',"022f",'024f','025f', "026f", "031f",'044f','045f', "048f",'049f','053f','054f','056f',"063f",'065f','070f') 
female_stim_data <- female_stim_data  %>%
  mutate(target = if_else(TargX == -0.45, l_image, r_image))

female_stim_data <- female_stim_data %>%
  mutate(targetraw = if_else(TargX == -0.45, l_image, r_image))

# Replace the entire cell with 'masculine' if it contains the word 'masc' etc
female_stim_data <- female_stim_data %>%
  mutate(target = if_else(str_detect(target, "masc"), "Low Dimorphism", target))

female_stim_data <- female_stim_data %>%
  mutate(target = if_else(str_detect(target, "fem"), "High Dimorphism", target))

female_stim_data <- female_stim_data %>%
  mutate(target = if_else(str_detect(target, "avg"), "Average", target))

female_stim_data <- female_stim_data %>%
  mutate(target = if_else(str_detect(target, "dist"), "Distinctive", target))

female_stim_data <- female_stim_data %>%
  mutate(target = if_else(str_detect(target, "/sym"), "Symmetrical", target))

female_stim_data <- female_stim_data %>%
  mutate(target = if_else(str_detect(target, "/asym"), "Asymmetrical", target))

#Trial remove tracker
initial_row_count <- nrow(female_stim_data)
cat("trial count:", initial_row_count, "\n")

#Remove reaction times that are too slow/fast (check values w/ jason)
female_stim_data <- female_stim_data %>% filter(SaccadicRTms > 50)

female_stim_data <- female_stim_data %>% filter(SaccadicRTms < 2000)

rows_after_trial_filter <- nrow(female_stim_data)
cat("Trials removed as SRTs too fast or slow :", initial_row_count - rows_after_trial_filter, "\n")

cat("% of Trials removed as SRTs too fast or slow :", (initial_row_count - rows_after_trial_filter)/initial_row_count*100, "\n")

row_count = nrow(female_stim_data)

cat("Final trial count:", row_count, "\n")


```

```{r}
cleaned_data_small <- rbind(male_stim_data,female_stim_data)
```


```{r Optional DFs}
#OPTIONAL
df_avg <- cleaned_data_small %>% filter(target %in% c("Average", "Distinctive"))
df_symmetrical <- cleaned_data_small %>% filter(target %in% c("Symmetrical", "Asymmetrical"))
df_sexdmph <- cleaned_data_small %>% filter(target %in% c("Masculine", "Feminine"))

malestim_df_avg <- male_stim_data %>% filter(target %in% c("Average", "Distinctive"))
malestim_df_symmetrical <- male_stim_data %>% filter(target %in% c("Symmetrical", "Asymmetrical"))
malestim_df_sexdmph <- male_stim_data %>% filter(target %in% c("Masculine", "Feminine"))

femalestim_df_avg <- female_stim_data %>% filter(target %in% c("Average", "Distinctive"))
femalestim_df_symmetrical <- female_stim_data %>% filter(target %in% c("Symmetrical", "Asymmetrical"))
femalestim_df_sexdmph <- female_stim_data %>% filter(target %in% c("Masculine", "Feminine"))

```
#################################################################
                          RATINGS Data
```{r Ratings dataset}
Ratings_data <- combined_df %>% select(participant, trial,female, male, Attractiveness.response, Symmetry.response,Beauty.response,Averageness.response, masculinity.response,femininty.response)

Ratings_data <- Ratings_data %>%
  mutate(targetsex = if_else(participant %in% c('pp1', 'pp4','pp7','pp9','pp11','pp10','pp16','pp17','pp21','pp23','pp26','pp28','pp29','pp30','pp32','pp33','pp36','pp37','pp38'), 'Male', 'Female'))

Ratings_data <- na.omit(Ratings_data)

Ratings_data <- Ratings_data %>%
  mutate(across(everything(), ~ na_if(., 'None')))


for (i in 1:nrow(Ratings_data)) {
  if (Ratings_data$targetsex[i] == "Male") {
    Ratings_data$female[i] <- NA
  } else if (Ratings_data$targetsex[i] == "Female") {
    Ratings_data$male[i] <- NA
  }
}


# Create the 'counterpart' column
Ratings_data$counterpart <- NA

# Initialize a counter to track changes
changes_made <- 0



for (i in 1:nrow(Ratings_data)) {
  # Check if the targetsex is "female"
  if (Ratings_data$targetsex[i] == "Female") {
    # Initialize counterpart with the original female value
    counterpart_value <- Ratings_data$female[i]
    
    # Perform the necessary replacements 
    counterpart_value <- gsub("asym", "TEMP1", counterpart_value)
    counterpart_value <- gsub("sym", "asym", counterpart_value)
    counterpart_value <- gsub("TEMP1", "sym", counterpart_value)
    counterpart_value <- gsub("masc", "TEMP2", counterpart_value)
    counterpart_value <- gsub("fem", "masc", counterpart_value)
    counterpart_value <- gsub("TEMP2", "fem", counterpart_value)
    counterpart_value <- gsub("avg", "TEMP3", counterpart_value)
    counterpart_value <- gsub("dist", "avg", counterpart_value)
    counterpart_value <- gsub("TEMP3", "dist", counterpart_value)
    
    
    # Assign the final counterpart value to the dataframe
    Ratings_data$counterpart[i] <- counterpart_value
  }
}


for (i in 1:nrow(Ratings_data)) {
  # Check if the targetsex is "male"
  if (Ratings_data$targetsex[i] == "Male") {
    # Initialize counterpart with the original male value
    counterpart_value <- Ratings_data$male[i]
    
    # Perform the necessary replacements 
    counterpart_value <- gsub("asym", "TEMP1", counterpart_value)
    counterpart_value <- gsub("sym", "asym", counterpart_value)
    counterpart_value <- gsub("TEMP1", "sym", counterpart_value)
    counterpart_value <- gsub("masc", "TEMP2", counterpart_value)
    counterpart_value <- gsub("fem", "masc", counterpart_value)
    counterpart_value <- gsub("TEMP2", "fem", counterpart_value)
    counterpart_value <- gsub("avg", "TEMP3", counterpart_value)
    counterpart_value <- gsub("dist", "avg", counterpart_value)
    counterpart_value <- gsub("TEMP3", "dist", counterpart_value)
    
    
    # Assign the final counterpart value to the dataframe
    Ratings_data$counterpart[i] <- counterpart_value
  }
}

# Create a lookup table
lookup_table <- Ratings_data %>%
  select(participant, male, Attractiveness.response) %>%
  rename(counterpart_attractiveness = Attractiveness.response,
         counterpart = male)

lookup_table2 <- Ratings_data %>%
  select(participant, female, Attractiveness.response) %>%
  rename(counterpart_attractiveness = Attractiveness.response,
         counterpart = female)

# Merge the original data with the lookup table to add the counterpart attractiveness response
Ratings_data <- Ratings_data %>%
  left_join(lookup_table, by = c("counterpart", 'participant'))

Ratings_data <- Ratings_data %>%
  left_join(lookup_table2, by = c("counterpart", 'participant'))

# View the updated dataframe
print(Ratings_data)

write.csv(Ratings_data, file = 'G:/Experiment/Experiment/ratings_data.csv', row.names = F )



```

```{r Split ratings into M/F}
male_stim_ratings_data <- Ratings_data %>% filter(targetsex %in% c('Male'))

# Filter rows where participant is 'pp2', 'pp3', 'pp5', or 'pp6'
female_stim_ratings_data <- Ratings_data %>% filter(targetsex %in% c('Female'))

female_stim_ratings_data <- female_stim_ratings_data %>% select(-male)

male_stim_ratings_data <- male_stim_ratings_data %>% select(-female)

```

```{r rename to image type}

male_stim_ratings_data <- male_stim_ratings_data %>%
  mutate(image_type = male)

male_stim_ratings_data <- male_stim_ratings_data %>%
  mutate(image_type = if_else(str_detect(image_type, "dist"), "Distinctive", image_type))

male_stim_ratings_data <- male_stim_ratings_data %>%
  mutate(image_type = if_else(str_detect(image_type, "avg"), "Average", image_type))

male_stim_ratings_data <- male_stim_ratings_data %>%
  mutate(image_type = if_else(str_detect(image_type, "/sym"), "Symmetrical", image_type))

male_stim_ratings_data <- male_stim_ratings_data %>%
  mutate(image_type = if_else(str_detect(image_type, "asym"), "Asymmetrical", image_type))

male_stim_ratings_data <- male_stim_ratings_data %>%
  mutate(image_type = if_else(str_detect(image_type, "fem"), "Low Dimorphism", image_type))

male_stim_ratings_data <- male_stim_ratings_data %>%
  mutate(image_type = if_else(str_detect(image_type, "masc"), "High Dimorphism", image_type))

male_stim_ratings_data <- male_stim_ratings_data %>%
  mutate(image_type = if_else(str_detect(image_type, "original"), "Original", image_type))


#Now female set

female_stim_ratings_data <- female_stim_ratings_data %>%
  mutate(image_type = female)

female_stim_ratings_data <- female_stim_ratings_data %>%
  mutate(image_type = if_else(str_detect(image_type, "dist"), "Distinctive", image_type))

female_stim_ratings_data <- female_stim_ratings_data %>%
  mutate(image_type = if_else(str_detect(image_type, "avg"), "Average", image_type))

female_stim_ratings_data <- female_stim_ratings_data %>%
  mutate(image_type = if_else(str_detect(image_type, "/sym"), "Symmetrical", image_type))

female_stim_ratings_data <- female_stim_ratings_data %>%
  mutate(image_type = if_else(str_detect(image_type, "asym"), "Asymmetrical", image_type))

female_stim_ratings_data <- female_stim_ratings_data %>%
  mutate(image_type = if_else(str_detect(image_type, "fem"), "High Dimorphism", image_type))

female_stim_ratings_data <- female_stim_ratings_data %>%
  mutate(image_type = if_else(str_detect(image_type, "masc"), "Low Dimorphism", image_type))

female_stim_ratings_data <- female_stim_ratings_data %>%
  mutate(image_type = if_else(str_detect(image_type, "original"), "Original", image_type))


```

```{r Now for file names}
malenames <- c('095m','098m','100m','108m','110m',"113m",'114m','115m', "116m", "117m",'119m','121m', "123m",'129m','147m','148m','149m',"151m",'152m','154m') # Add all your patterns here

male_stim_ratings_data <- reduce(malenames, function(df, pattern) {
  df %>% mutate(male = if_else(str_detect(male, pattern), pattern, male))
}, .init = male_stim_ratings_data)

male_stim_ratings_data <- male_stim_ratings_data %>%
  select(-counterpart_attractiveness.y) %>%
  rename(counterpart_attractiveness = counterpart_attractiveness.x)

male_stim_data <- reduce(malenames, function(df, pattern) {
  df %>% mutate(
    l_image = if_else(str_detect(l_image, pattern), pattern, l_image),
    r_image = if_else(str_detect(r_image, pattern), pattern, r_image)
  )
}, .init = male_stim_data)


femalenames <- c('003f','008f','010f','019f','020f',"022f",'024f','025f', "026f", "031f",'044f','045f', "048f",'049f','053f','054f','056f',"063f",'065f','070f') # Add all your patterns here

female_stim_ratings_data <- reduce(femalenames, function(df, pattern) {
  df %>% mutate(female = if_else(str_detect(female, pattern), pattern, female))
}, .init = female_stim_ratings_data)

female_stim_ratings_data <- female_stim_ratings_data %>%
  select(-counterpart_attractiveness.x) %>%
  rename(counterpart_attractiveness = counterpart_attractiveness.y)


female_stim_data <- reduce(femalenames, function(df, pattern) {
  df %>% mutate(
    l_image = if_else(str_detect(l_image, pattern), pattern, l_image),
    r_image = if_else(str_detect(r_image, pattern), pattern, r_image)
  )
}, .init = female_stim_data)

```

```{r means}
# Define the columns of interest
columns_of_interest <- c("Attractiveness.response", "Symmetry.response", "Beauty.response", "Averageness.response", "masculinity.response", "femininty.response", 'counterpart_attractiveness')

male_stim_ratings_data[columns_of_interest] <- lapply(male_stim_ratings_data[columns_of_interest], as.numeric)

# Group by 'male' and 'image_type' and calculate means for specified columns
male_grouped_means <- male_stim_ratings_data %>%
  group_by(male, image_type) %>%
  summarize(across(all_of(columns_of_interest), mean, na.rm = TRUE), .groups = 'drop')

# View the resulting dataframe
print(male_grouped_means)
```

```{r female means}
female_stim_ratings_data[columns_of_interest] <- lapply(female_stim_ratings_data[columns_of_interest], as.numeric)

# Group by 'female' and 'image_type' and calculate means for specified columns
female_grouped_means <- female_stim_ratings_data %>%
  group_by(female, image_type) %>%
  summarize(across(all_of(columns_of_interest), mean, na.rm = TRUE), .groups = 'drop')

# View the resulting dataframe
print(female_grouped_means)
```
```{r highlight high values}
highlight_max_per_female <- function(df, columns) {
  df %>%
    group_by(female) %>%
    mutate(across(all_of(columns), ~ ifelse(.x == max(.x, na.rm = TRUE), paste0(.x, "*"), .x))) %>%
    ungroup()
}

highlight_max_per_male <- function(df, columns) {
  df %>%
    group_by(male) %>%
    mutate(across(all_of(columns), ~ ifelse(.x == max(.x, na.rm = TRUE), paste0(.x, "*"), .x))) %>%
    ungroup()
}




# Save the highlighted table as a CSV file for females
write.csv(female_grouped_means, file = "female_rating_means_highlighted_table.csv", row.names = FALSE)


# Save the highlighted table as a CSV file for males
write.csv(male_grouped_means, file = "male_rating_means_highlighted_table.csv", row.names = FALSE)





```

```{r RemoveFEMALE}
face_ratings_female <- read.csv("female_rating_means_highlighted_table.csv")

initial_ratings_count_female <- nrow(face_ratings_female)
cat("Total ratings count:", initial_ratings_count_female, "\n")

# Function to identify images to be removed based on specific conditions
identify_images_to_remove <- function(data) {
  images_to_remove <- data %>%
    group_by(female) %>%
    filter(femininty.response[image_type == "Low Dimorphism"] > femininty.response[image_type == "High Dimorphism"] |
           masculinity.response[image_type == "High Dimorphism"] > masculinity.response[image_type == "Low Dimorphism"] |
           Symmetry.response[image_type == "Asymmetrical"] > Symmetry.response[image_type == "Symmetrical"] |
           Averageness.response[image_type == "Distinctive"] > Averageness.response[image_type == "Average"]) %>%
    pull(female) %>%
    unique()
  
  return(images_to_remove)
}

# Function to remove identified images from a dataset
remove_images <- function(data, images_to_remove) {
  data_cleaned <- data %>%
    filter(!female %in% images_to_remove)
  
  return(data_cleaned)
}

remove_images_stim_data <- function(data, images_to_remove) {
  data_cleaned <- data %>%
    filter(!l_image %in% images_to_remove)
  
  return(data_cleaned)
}


# Identify images to be removed from the male and female datasets
images_to_remove_female <- identify_images_to_remove(face_ratings_female)

print(images_to_remove_female)

# Remove identified images from each dataset
cleaned_face_ratings_female <- remove_images(face_ratings_female, images_to_remove_female)
female_stim_data <- remove_images_stim_data(female_stim_data,images_to_remove_female)

rows_after_trial_filter <- nrow(cleaned_face_ratings_female)
cat("ratings removed as manipulation check was FALSE :", initial_ratings_count_female - rows_after_trial_filter, "\n")

cat("% of Trials removed as manipulation check was FALSE :", (initial_ratings_count_female - rows_after_trial_filter)/initial_ratings_count_female*100, "\n")

initial_ratings_count_female = nrow(cleaned_face_ratings_female)

cat("Final ratings count:", initial_ratings_count_female, "\n")

#  save the cleaned datasets to new CSV files
write.csv(cleaned_face_ratings_female, "cleaned_face_ratings_female.csv", row.names = FALSE)
```
```{r RemoveMALE}
# Load your datasets
face_ratings_male <- read.csv("male_rating_means_highlighted_table.csv")
initial_ratings_count_male <- nrow(face_ratings_male)
cat("Total ratings count:", initial_ratings_count_male, "\n")


# Function to identify images to be removed based on specific conditions
identify_images_to_remove <- function(data) {
  images_to_remove <- data %>%
    group_by(male) %>%
    filter(femininty.response[image_type == "High Dimorphism"] > femininty.response[image_type == "Low Dimorphism"] |
           masculinity.response[image_type == "Low Dimorphism"] > masculinity.response[image_type == "High Dimorphism"] |
           Symmetry.response[image_type == "Asymmetrical"] > Symmetry.response[image_type == "Symmetrical"] |
           Averageness.response[image_type == "Distinctive"] > Averageness.response[image_type == "Average"]) %>%
    pull(male) %>%
    unique()
  
  return(images_to_remove)
}

# Function to remove identified images from a dataset
remove_images <- function(data, images_to_remove) {
  data_cleaned <- data %>%
    filter(!male %in% images_to_remove)
  
  return(data_cleaned)
}

remove_images_stim_data <- function(data, images_to_remove) {
  data_cleaned <- data %>%
    filter(!l_image %in% images_to_remove)
  
  return(data_cleaned)
}


# Identify images to be removed from the male and male datasets
images_to_remove_male <- identify_images_to_remove(face_ratings_male)

print(images_to_remove_male)

# Remove identified images from each dataset
cleaned_face_ratings_male <- remove_images(face_ratings_male, images_to_remove_male)
male_stim_data <- remove_images_stim_data(male_stim_data,images_to_remove_male)

rows_after_trial_filter <- nrow(cleaned_face_ratings_male)
cat("ratings removed as manipulation check was FALSE :", initial_ratings_count_male - rows_after_trial_filter, "\n")

cat("% of Trials removed as manipulation check was FALSE :", (initial_ratings_count_male - rows_after_trial_filter)/initial_ratings_count_male*100, "\n")

initial_ratings_count_male = nrow(cleaned_face_ratings_male)

cat("Final ratings count:", initial_ratings_count_male, "\n")

# save the cleaned datasets to new CSV files
write.csv(cleaned_face_ratings_male, "cleaned_face_ratings_male.csv", row.names = FALSE)

# Merge the original data with the lookup table to add the counterpart attractiveness response
cleaned_face_ratings_female <- cleaned_face_ratings_female %>%
  rename(ID = female)
cleaned_face_ratings_male <- cleaned_face_ratings_male %>%
  rename(ID = male)

Ratings_data_cleaned <- cleaned_face_ratings_male %>%
  rbind(cleaned_face_ratings_female)

Ratings_data <- Ratings_data %>%
  left_join(lookup_table2, by = c("counterpart", 'participant'))

# View the updated dataframe
print(Ratings_data)
write.csv(Ratings_data_cleaned, file = 'G:/Experiment/Experiment/ratings_data_cleaned.csv', row.names = F)
write.csv(Ratings_data, file = 'G:/Experiment/Experiment/ratings_data.csv', row.names = F)
```
```{r add attracitveness and beauty ratings to the DF}

# Select relevant columns and rename them for consistency
categorized_ratings <- male_stim_ratings_data %>%
  select(participant, Attractiveness.response, counterpart_attractiveness, Beauty.response, male, image_type) %>%
  rename(l_image = male, target = image_type)

# Merge the categorized ratings with the main dataframe based on the participant key
male_stim_data <- male_stim_data %>%
  left_join(categorized_ratings, by = c('participant', 'l_image', 'target'))

# Print the first few rows of the updated data
head(male_stim_data)
```

```{r}

# Select relevant columns and rename them for consistency
categorized_ratings <- female_stim_ratings_data %>%
  select(participant, Attractiveness.response, counterpart_attractiveness, Beauty.response, female, image_type) %>%
  rename(l_image = female, target = image_type)

# Merge the categorized ratings with the main dataframe based on the participant key
female_stim_data <- female_stim_data %>%
  left_join(categorized_ratings, by = c('participant', 'l_image', 'target'))

# Print the first few rows of the updated data
head(female_stim_data)
```

```{r}
cleaned_data_removed_ratings <- rbind(male_stim_data, female_stim_data)
```

```{r}
write.csv(cleaned_data, file = 'G:/Experiment/Experiment/cleaned_data.csv', row.names = F)

write.csv(cleaned_data_removed_ratings, file = 'G:/Experiment/Experiment/cleaned_data_removed_ratings.csv', row.names = F )

write.csv(female_stim_data, file = 'G:/Experiment/Experiment/female_stim_data.csv', row.names = F)

write.csv(male_stim_data, file = 'G:/Experiment/Experiment/male_stim_data.csv', row.names = F )
```
